---
title: "Collaboration"
author: "Zarah Khan, Haykal Mubin, Jessica Prasetyo, George Zhang, Jeremy Lin"
date: "2/24/2019"
output: html_document
---
## Small Countries are Beautiful: Analysis

```{r setup,echo=FALSE,message=FALSE}
source("chart1.R")
source("chart2.R")
source("chart3.R")
source("summary.R")
```

```{r george, echo=FALSE, message=FALSE}
summary_information <- summary("WDVP Datasets - small countries are beautiful 6.51.37 PM.csv")
```
The data in this report is from the **World Data Vizualization** competition and discusses the 
dataset titled _Small Countries are Beautiful_. The dataset deals with small nations with a population of less than **five million** people that are "often overshadowed by statistics". The creators of the data set felt like these developing nations weren't recognized very often in the areas of innovation or growth and felt like there was a lot to learn from the various information about them.  

We can see a clear correlation betweeen development of a country and its happiness score in the charts below. In this chart, notice how the more developed countries (in pink) have a higher mean happiness, just above a "7". Meanwhile, less developed countries have a lower happiness score below a "5". This gives us insight into the argument that the more developed a country is, the happier it is. This is likely because the people that live in that country have more access to resources that satisfy their needs. 

```{r jeremy, echo=FALSE}
plot_3("WDVP Datasets - small countries are beautiful 6.51.37 PM.csv")
```

According to [Maslow's hierarchy of needs](https://en.wikipedia.org/wiki/Maslow%27s_hierarchy_of_needs) from the psychology theory proposed by Abraham Maslow, humans have the following  needs:  "physiological," "safety," "belonging and love," or "social needs" "esteem," and "self-actualization". In less developed countries, all these basic needs might not be met for the people living there which may indicate why its citizens are not scoring as high on mean happiness. 

For example,  the country with the most GDP is `r summary_information$max_GDP_country` with a GDP of `r summary_information$max_GDP` , unsurprisingly, `r summary_information$max_GDP_country` is also a part of the list of the top "happiest" countries which includes : `r summary_information$happy_top5` . This relates to [Maslow's hierarchy of needs](https://en.wikipedia.org/wiki/Maslow%27s_hierarchy_of_needs) because money is a means to an end of satisfying "physiological" needs (such as food, water, sleep, shelter etc.) and other kinds of needs such as safety (health/well being, financial security) and self-actualization (education etc.). 


```{r jessica, echo=FALSE, message=TRUE, warning=FALSE}
my_plot("WDVP Datasets - small countries are beautiful 6.51.37 PM.csv")
```

```{r haykal, echo=FALSE}
scatter_plot("WDVP Datasets - small countries are beautiful 6.51.37 PM.csv")
```







